Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-05-23 paper/conclusion.tex
conclusion

In this work, we explored the back-to-back (B2B) regression, a novel method for
identifying causes from observations building on two successive
multidimensional regressions; from one domain to the other, and then back.
We analyzed the asymptotic behavior of this approach, proving its convergence,
and compared it to several baselines in controlled synthetic experiments. We
showcased our approach on a recent brain imaging dataset, analyzing the timing
of brain responses and their connection to features of words, and obtained
results consistent with prior work in neuroscience literature, confirming the
viability of our method in the case of real data.

>>>>

In this work, we proposed Back-to-Back (B2B) regression, a linear method to
measure the causal influence of a potential set of variables generating multidimensional observations.
%
B2B performs two successive multidimensional regressions: one from the output domain, and another one from the input domain.
%
We provided a theoretical guarantee about the consistency of B2B, and compared it to several baselines in controlled synthetic experiments.
%
We also applied B2B to a recent brain imaging dataset, analyzing the timing
of brain responses and their connection to word features.
%
We obtained results consistent with prior work in neuroscience literature, confirming the efficacy of B2B for real data analysis.
%
